Notebook with AMP-AD RNA-seq network analysis results

### 2020-01-03 manuscript.Rmd
magma and upset updates

@@

>>>>

Show that the aggregate modules are better enriched than other potential AD modules (Figure 1A)

```{r}
synapser::synLogin()
g <- AMPAD::improvedAdRelevancePlot()
g
```

Show summaries of overlaps with UpSet plots (Figure S1A-S1E)

```{r}
synapser::synLogin()
res<-AMPAD::aggregate_module_summary_plots()
res
```

@@

Run MAGMA analysis (must have magma tool installed in current working directory that this notebook is running from), producing the plot from Figure S1F
```{r}
synapser::synLogin()
g <- AMPAD::run_magma_analysis()
g
```
